Consistency scores in text data

### 2020-08-28 outputs/documents/paper.Rmd
aRianna bug documentation

We consider various natural language processing methods. These include n-grams, Word2Cec, GloVe, GPT models and BERT. The n-gram approach involves identifying two, three, or more, words that are commonly found together. Here think of a two-gram involving the word 'good' 'good morning'. At scale these can identify missing or unusual words, and work quickly, but they lack nuance. For instance, an equally reasonable two-gram involving the word 'good' is 'good work'. For that reason, we consider pre-trained word embedding models. These include Word2Vec and GloVe, which place each word in a multi-dimensional space such that distance between words can illustrate their relationship. We also consider pre-trained generative models such as GPT-2 and GPT-3 and BERT. GPT-2, GPT-3 and BERT are pre-trained generative unsupervised language models. GPT-2 and GPT-3 are the two generations of the same model that differ in the number of parameters. GPT-2 has 1.5 billion parameters and GPT-3 has more than 175 billion parameters. While GPT-2 is more limited, it can be run on smaller machines, whereas GPT-3 cannot and is accessed via an API. BERT has 340 millions parameters which is smaller than both GPT-2 and GPT-3. BERT also differs from GPT models because its encoding process is bidirectional instead of unidirectional.

@@

The implementation of text correction with BERT in R with the `keras-bert` Python module is not yet completed. For the purpose of demonstrating how BERT predicts the missing words, we will show the implementation process in Python using the `pytorch_pretrained_bert` library. The reason to use `pytorch_pretrained_bert`(**Keli add citation**) instead of `keras-bert`is that `pytorch_pretrained_bert` has relatively comprehensive functions that makes the prediction of missing words more straightforward.

>>>>

We consider various natural language processing methods. These include n-grams, Word2Vec, GloVe, GPT models and BERT. The n-gram approach involves identifying two, three, or more, words that are commonly found together. Here think of a two-gram involving the word 'good' 'good morning'. At scale these can identify missing or unusual words, and work quickly, but they lack nuance. For instance, an equally reasonable two-gram involving the word 'good' is 'good work'. For that reason, we consider pre-trained word embedding models. These include Word2Vec and GloVe, which place each word in a multi-dimensional space such that distance between words can illustrate their relationship. We also consider pre-trained generative models such as GPT-2 and GPT-3 and BERT. GPT-2, GPT-3 and BERT are pre-trained generative unsupervised language models. GPT-2 and GPT-3 are the two generations of the same model that differ in the number of parameters. GPT-2 has 1.5 billion parameters and GPT-3 has more than 175 billion parameters. While GPT-2 is more limited, it can be run on smaller machines, whereas GPT-3 cannot and is accessed via an API. BERT has 340 millions parameters which is smaller than both GPT-2 and GPT-3. BERT also differs from GPT models because its encoding process is bidirectional instead of unidirectional.

@@

The implementation of text correction with BERT in R with the `keras-bert` Python module is not yet completed. For the purpose of demonstrating how BERT predicts the missing words, we will show the implementation process in Python using the `pytorch_pretrained_bert` library. The reason to use `pytorch_pretrained_bert` [@Wolf2019HuggingFacesTS] instead of `keras-bert`is that `pytorch_pretrained_bert` has relatively comprehensive functions that makes the prediction of missing words more straightforward.
